### 2014-05-18 tex/main-body-text.tex
Combined all Q-val plots into a single axis
Edited the results section and added Fig1 in Grey Scale

\subsection*{Results} 
Run times were relatively short for both programs. The six groups of runs for {\sc flock} 
using the default settings required 1133 minutes to complete. Each individual group  of runs 
averaged 188.8 minutes (1.5 min SD). The six iterations of {\sc structure} completed in 
XXXX minutes with each iterations averaging XXXX (SD).

While no  plateaus were observed in any of the six groups for a \textit{k} greater than 
two, the plateau record varied greatly among each
 group for \textit{k}=2 (plateau  sequences- Run1= 3,2,3,7,4; Run2=2,5,2,3,2,3; Run3=2,2,2,2,2,5; 
Run4=2,3,4,2,4,3; Run5=2,2,5,5,3; and; Run6=2,2,2,2,2,3,3). The plateau analysis 
procedure suggested by \citet{Duc&Tur2012} leads to 
either an estimate of K$\geq$2 or \textit{undecided} as a consequence of no plateau 
lengths being greater than 6. Distruct plots for each group of runs for \textit{k}=2-4 
lead to nearly identical clustering of individuals (See supplementary materials). While 
only two of the six 'best runs' when 
\textit{k}=2 ended with identical clustering (same mean LLOD score), all other runs 
differed by at most the allocation of 13 individuals. When \textit{k} was set to three 
and four all runs provided very similar clustering.

@@

With increased \textit{k} {\sc flock} continues to splits individuals approximately 
based on geographical boundaries identified by \citet{Garzaetal_norcal} using {\sc 
structure}.

\begin{figure*}
\begin{center}
    \includegraphics[width=\textwidth]{images/Figures-Pat/Qval-StrFloc.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for \textit{k}=5. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{Fig.2}
\end{center}
\end{figure*}

>>>>

\subsection*{Results} 
Run times were relatively short for both programs. The six groups of runs for {\sc flock} 
required 1133 minutes to complete. Each individual group of runs 
averaged 188.8 minutes (1.5 min SD). The six iterations of {\sc structure} completed in 
486 minutes with each of the six iterations averaging 80.8 minutes (0.8 min SD). Increasing
the number of putative clusters from \textit{k} of two to six yielded a 2.4 fold increase 
in processing time for {\sc flock}, whereas a 1.6 fold increase was observed for runs of 
{\sc structure}.

The allocation of indivividuals into K clusters is congruent for each program. For all six groups 
of runs from \textit{k}=2-4, {\sc flock} lead to nearly identical clustering of individuals 
(See supplementary materials). It should be noted
that of the 50 starting allocations of individuals in the {\sc flock} procedure only the LLOD for the 
 'best run' is reported. Of these 'best runs' for a \textit{k} of 2 only two  
ended with identical clustering (same mean LLOD score), all other runs 
differed by at most the allocation of 13 individuals. As \textit{k} increases so do the number of solutions
that {\sc flock} finds (Fig 1). These solutions, however, are suprisingly similar to
 the partions identified by {\sc structure}. Both programs idenfity clusters 
which can be attributed to the geographical boundaries identified by \citet{Garzaetal_norcal}.

Despite the similar allocation of individuals into \textit{k} clusters, the 
plateau analysis in {\sc flock} leads to different conclusions among groups of runs, as well as 
one that differs from both the pure likelihood 
and delta K approach in {\sc structure}. While no plateaus were observed in any of the six groups 
for a \textit{k} $\geq$2, the plateau record varied greatly among each
 group for \textit{k}=2 (plateau  sequences- Run1= 3,2,3,7,4; Run2=2,5,2,3,2,3; Run3=2,2,2,2,2,5; 
Run4=2,3,4,2,4,3; Run5=2,2,5,5,3; and; Run6=2,2,2,2,2,3,3). The plateau analysis 
procedure suggested by \citet{Duc&Tur2012} leads to 
either an estimate of K$\geq$2 (Run1) or \textit{undecided} as a consequence of no plateau 
lengths being greater than 6. Interpreting the results from {\sc structure} can either be done 
with the estimated likelihood of the data from the program itself or by the delta k method 
suggest by Evanno et al XXXXX. Both methods indicate that the most likely \textit{k} for the dataset is 6.

@@

\begin{figure*}
\begin{center}
	% NOTE. Pat made Q-val-StrFloc.pdf that has all runs individually, replaced with 
	% all of them on same axis. It will look fine as a black and white with different 
	% characters.
 \includegraphics[width=\textwidth]{images/Figures-Pat/Qval-1plot.pdf}
    \caption{Individual \textit{$q_i$} values plotted for each cluster for \textit{k}=5. 
{\sc flock} estimates of likelihood of assignment to each cluster have less uncertainty
 attributed to them.}
    \label{Fig.2}
\end{center}
\end{figure*}
